---
title: "HW6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
library(tidyverse)
library(rstanarm)
library(lme4)
options(mc.cores = parallel::detectCores())
```

Recall the butterfly movement dataset from 505. Here we consider the entire set of step distances, rather than just a single one for each butterfly.

```{r}
butterfly <- read_csv('butterfly_move.csv') %>%
  filter(!is.na(Step_Distance))
```

#### Q1. (4 points)
Compute the average step distance for each butterfly. Show the results (or a subset of them) visually. (4 points)

#### Q2. (4 points)
Write out a hierarchical (or multilevel or mixed model) for a model that fits a different average for butterfly. 

### Q3. (6 points)
Fit a hierarchical (or multilevel or mixed model) for a model that fits a different average for butterfly. Report estimated values (with uncertainty) for all of the parameters in your model. 

### Q4. (6 points)
Plot and comment (_the what and why_) about the comparison between the raw mean distance traveled and estimates from the hierarchical model for the following butterflies. (6 points)

```{r}
display_butterflies <- tibble(Track.num = c(161, 162, 163, 164))
```

